---
title: "A fancy report"
output: html_document
params:
  species: "Gentoo"
  title: "Important Penguin Plot"
  description: "default text"
  regex: "o"
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(gt)
```


# Parent Doc

This is a report about fancy penguins.

If the condition is met we can add in our specific child document.

```{r dayOfWeek}
day_of_week <- lubridate::ymd(Sys.Date()) %>% 
  wday(label= TRUE) %>% 
  as.character()
day_of_week
```

---

# Can use `results='asis'`

If you just want to add a title and some text, `results='asis'` in a chunk + `cat()` is a quick and easy option.

This option just used to generate some of the text inline, as opposed to all the plots/etc.

```{r asisDoc, echo = FALSE, results='asis'}
if(day_of_week %in% c("Mon", "Tues")){
  glue::glue(
    "### {params$title}",
    "\n",
    "{params$description}"
  ) %>% 
    cat(sep = "\n")
}
```

---

# Use of Child report

This will be used to generate a more complex output with tables, plots, etc, and a child RMarkdown.

```{r childReport, child=if(day_of_week %in% c("Mon", "Tues"))'child-report.Rmd'}
```

---

# Alternate with use of `whisker`

This reads in a RMarkdown, fills all the components where `{{ }}` are observed, and then writes out the components. Note that you need to wrap text with `"` to get the correct outputs, and you need to pass the outputs more directly, since `whisker` is "logicless" it can't parse R code, but rather just R objects.

```{r whiskerDoc, echo = FALSE, results = 'asis'}
if(day_of_week %in% c("Mon", "Tues")){
  # have to extract the params ahead of time 
  # and then feed them into whisker
  
  input_title <- params$title
  input_species <- params$species
  input_desc <- params$description
  input_regex <- params$regex
  raw_text <- readLines("whisker-child.Rmd")
  filled_text <- whisker::whisker.render(raw_text)
  
  # now we can use our 'in memory' child RMarkdown
  # that has been filled and generate the output
  whisker_output <- knitr::knit_child(
    text = filled_text, 
    envir = environment(), 
    quiet = TRUE
    )
  
  cat(whisker_output, sep = "\n")
}
```

